Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-13 ms.tex
I adjusted the intro to describe some of the attributes of the KIC 1255 light curve.

\section{Introduction}
The disintegrating planet candidate KIC 12557548 b (hereafter \sha) \citep{rappaport} was the first discovery of a planet candidate causes stochastically varying dust obscuration of its host star.
It is now one of many systems that have stochastically varying transit depths.
The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and can have wavelength-dependent transmission predicted for dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.
Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still multiple explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.

>>>>

\section{Introduction}
\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
The KIC 12557548 (hereafter \shStar) light curve exhibited periodic flux dips with a period of 0.653 days.
What was highly unusual about \shStar\ was that the flux dips were neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
The variations in amplitude are highly stochastic and unpredictable from one event to the next 0.653 days later.
This indicates the creation and destruction of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
These variable dips are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.

The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.

Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still multiple explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
